---
title: "Personal Loan Acceptance"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Raj Kumar Pandit

### BL.BU.P2EMB19008

### Business Analytics 1

#### Department of Management
#### Amrita Vishwa Vidyapeetham (University)


***


## Libraries Used

```{r warning=FALSE, results = 'hide'}
library(knitr)
library(markdown)
library(dplyr)
library(GGally)
library(tidyverse)
```

## Setting up the local location

```{r warning=FALSE, results = 'hide'}
getwd()
setwd('C://TCSInternals//AmritaSUNY-Buffalo//Courses//BA-1//assignment_1')
```

## Data

Loading the file into R studio
```{r warning=FALSE}
ubank.df<-read.csv("UniversalBank.csv")
```

## Introduce the case by applying dim() and str().

Dimension
```{r warning=FALSE}
dim(ubank.df)
```
It has 5000 rows and 14 columns

## Explain all demographic variables i.e. age, experience, and income

Structure of the variables whose values fill the columns of the file

```{r warning=FALSE}
str(ubank.df)
```

### Data snapshot

```{r warning=FALSE}
head(ubank.df)
```

### Visualizing categorical variable 'education'

Cross Table

```{r warning=FALSE}
edu<- factor(ubank.df$Education, c(1,2,3),labels = c('Undergraduates','Graduate', 'Professional'))
edu_Tab<- table(edu)
addmargins( edu_Tab)
```

Cross Table with Percent Data

```{r warning=FALSE}
addmargins(round(100*prop.table(edu_Tab),digits=0))
```
### Bar chart

```{r warning=FALSE}
barplot(edu_Tab, xlab='Education Level',ylab='Frequency',main="Education Data Distribution",
         col=c('olivedrab2', 'orange1','purple2'), ylim = c(0,2500))
```

Bar char correctly concides with data represented in cross table

## Scatter plot between Age, Experience, Income, and CCAvg

Getting subset of data

```{r warning=FALSE}
aeic.df<-select ( ubank.df, c(Age, Experience, Income, CCAvg ))
summary(aeic.df)
plot(density(aeic.df$Age), main = 'Density plot of Age')
plot(density(aeic.df$Experience), main = 'Density plot of Experience')
plot(density(aeic.df$Income), main = 'Density plot of Income')
plot(density(aeic.df$CCAvg), main = 'Density plot of CCAGV')

```

Drawing scatter plot using 'GGally'

```{r warning=FALSE}

ggpairs(aeic.df)
```

## Boxplot of The Income Variable 

```{r warning=FALSE}
boxplot(ubank.df$Income, horizontal = TRUE, axes = TRUE, staplewex = 1)
text(x=fivenum(ubank.df$Income), labels =fivenum(ubank.df$Income), y=1.25)
```

### for drawing box plot

```{r warning=FALSE}
min(ubank.df$Income)
max(ubank.df$Income)
quantile(ubank.df$Income)
```

## Probability Calculation

### (1)  P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors)

```{r warning=FALSE}
pLoan <-which(ubank.df$Personal.Loan == 1)

```
ppLoan this has all the indices where values ==1 thus n[y=1] is calculated

```{r warning=FALSE}
sum(ubank.df$CreditCard[pLoan] ==1)/length(pLoan)

```

This ratio of n[cc = 1 INTERSECT Loan = 1] / n[Loan==1]
 
### (2)  P(Online = 1 | Loan = 1)

```{r warning=FALSE}
sum(ubank.df$Online[pLoan] ==1)/length(pLoan)
```
 this ratio of n[Online ==1 INTERSECT Loan = 1] / n[Loan==1]

### (3) P(Loan = 1) (the proportion of loan acceptors)

```{r warning=FALSE}
length(pLoan)/dim(ubank.df)[1]
```

### (4) P(CC = 1 / Loan = 0)

```{r warning=FALSE}
pLoanZero <-which(ubank.df$Personal.Loan == 0)
sum(ubank.df$CreditCard[pLoanZero] ==1)/length(pLoanZero)
```

### (5) P(Online = 1 / Loan = 0)

```{r warning=FALSE}
sum(ubank.df$Online[pLoanZero] ==1)/length(pLoanZero)
```

### (6) P(Loan = 0)

```{r warning=FALSE}
length(pLoanZero)/dim(ubank.df)[1]
```

